\documentclass{resume}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Nasif Mauthoor} % Your name
\address{North of the Wall, Outside the reach of every kingdom}
\address{(+0)9999999999 \\ nasifmrmonline@gmail.com}

\begin{document}

    \begin{rSection}{}

        \begin{center}
            A bright Computer Engineering student with aspirations in
            robotics and software development.
        \end{center}

    \end{rSection}

    \begin{rSection}{Education}

        \textbf{University of Guelph, Canada}
        \hfill{\em September 2019 - Present}
        \\ Bachelor of Engineering, Computer Engineering.
        \hfill{Overall: TBD - Current GPA: 3.0}

        \textbf{École Secondaire Jeunes Sans Frontières}
        \hfill {\em September 2019 - Present}
        \\ French High School Diploma.
        International Baccalaureate.
        \hfill { Overall GPA: 3.9}

    \end{rSection}

    \begin{rSection}{Significant Projects}

        A full list of other notable projects and works with full descriptions
        and documentation can be found on my GitHub page, which is continuously
        being updated (github.com/MoonJumpMania).

        \textbf{Terminal Shell Simulator}
        \\ A computer shell that can functionally do the basics of what the GNU
        Bash shell can like execute commands, piping IO and running processes in
        the background.
        Solution written in \textbf {C}.

        \textbf{CPU and Memory Scheduling Simulator}
        \\ A Discrete Event Scheduler that can manage the execution of threads
        and processes using various scheduling algorithms such as Round Robin and
        First-Come-First-Serve.
        The Memory scheduler kicks processes in and out of memory in method of
        choice between algorithms such as Best-Fit, Worst-Fit, First-Fit and
        Next-Fit.
        Both Schedulers were written in \textbf {C}.

        \textbf{VHDL CPU Simulator}
        \\ A basic virtual CPU that takes advantage of registers, memory and
        multiplexers to execute \textbf{Mars MIPS} assembly commands store data
        in memory and registers.
        Written in \textbf{VHDL}.

        \textbf{Cellular Automata}
        \\ A recreation Conway's Game of Life.
        Later used this method to create an algorithm to generate randomized
        terrain generation.
        Written in \textbf{C}.

        \textbf{Fluid Physics Simulator}
        \\ A simulation of liquids moving on different surfaces in a 2D space.
        Written in \textbf{C\#} using the \textbf{Unity} game engine.

        \textbf{Ludum Dare Game Jam}
        \\ A game jam where I had to build games in one single weekend.
        Created a game to teach about ecology and the pairing of animal species.
        Created a second game showing how a 3D space can be visualised in two
        dimensions.
        Worked alone and as a team.
        Both written in \textbf{C\#} using the \textbf{Unity} game engine.

        \textbf{Colossal Cave Adventure}
        \\ A recreation of Will Crowther's game from 1976.
        Written in \textbf{Java} using the \textbf{Swing} framework.

        \textbf{Discord Utility Bot}
        \\ A Discord application that can run on any Discord server to play
        music, read and write suggestions from and to files and do some basic
        automation.
        Written in \textbf{Python} using the \textbf{discord.py} API\@.

        \textbf{Basketball Playing Robot}
        \\ A school project at University of Guelph called Teddy Bear Wheelchair.
        The wheelchair robot needs to carry around a teddy bear and have it
        shoot ping-pong balls at a basketball net with precise accuracy and have
        it run a course designed to test its mobility.
        Written in \textbf{C++} powered by \textbf{Arduino}.

    \end{rSection}
%
%
% \newpage
    \begin{rSection}{Technical Strengths}

        \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
            Languages \         & C, C++, Python, Java, C\#    \\
            Technologies       & MVC, HTML5, CSS, Latex       \\
            Tools              & MikTex, Kile, Netbeans       \\
            Databases          & MySql, Oracle, Sqlite, NoSql \\
            Cloud Technologies & Firebase, AWS, Google Cloud  \\
            Version Control    & Github
        \end{tabular}

    \end{rSection}

    \begin{rSection}{Work Experience}
        \begin{rSubsection}{Reversible Alphabet Pvt. Ltd., India}{Jun 2017 - Dec 2018}{Data Scientist}{}
            \item Created classification models for e-commerce websites using neural networks.
            \item Achieved exposure towards classification optimaization techniques for further specialization.
            \item Worked under an experenced Data Scientist and got deep insights related to optimization algorithms.
        \end{rSubsection}
        \begin{rSubsection}{Irreversible Alphabet Pvt. Ltd., India}{Jun 2016 - Dec 2016}{Data Scientist}{}
            \item Created classification models for e-commerce websites using neural networks.
            \item Achieved exposure towards classification optimaization techniques for further specialization.
            \item Worked under an experenced Data Scientist and got deep insights related to optimization algorithms.
        \end{rSubsection}

    \end{rSection}
% 
    \newpage
    \begin{rSection}{Academic Achievements}
        \item Project 'XYZ' won Best Project under Environmental Solver category under AICTE, Government of India
        \item Recieved Scholarship For Higher Education(She) Component Under Inspire Scheme worth INR 4,00,000
        \item Achived A Grade in Diploma in Computer Science from IBM
        \item Won First Prize in Zonal technical quiz Competition Organized by IIT, Mumbai.
        \item Project 'XYZ' won Best Project under Environmental Solver category under AICTE, Government of India
        \item Recieved Scholarship For Higher Education(She) Component Under Inspire Scheme worth INR 4,00,000
        \item Achived A Grade in Diploma in Computer Science from IBM
        \item Won First Prize in Zonal technical quiz Competition Organized by IIT, Mumbai.
    \end{rSection}

    \begin{rSection}{Extra-Cirrucular}
        \item Attended a workshop on Machine Learning and artificial intelligence from faculties of IIT Roorkee in 2019 and won zonal round for the challenge presented.
        \item Member of the Institute of Engineers since 2017.
        \item Completed Basic Leadership Training under Project NSS, Gujarat
        \item Attended a workshop on Machine Learning and artificial intelligence from faculties of IIT Roorkee in 2019 and won zonal round for the challenge presented.
        \item Member of the Institute of Engineers since 2017.
        \item Completed Basic Leadership Training under Project NSS, Gujarat
        \item Attended a workshop on Machine Learning and artificial intelligence from faculties of IIT Roorkee in 2019 and won zonal round for the challenge presented.
        \item Member of the Institute of Engineers since 2017.
        \item Completed Basic Leadership Training under Project NSS, Gujarat

    \end{rSection}
    \begin{rSection}{Research Profile}
        \item Student President, Technology and Research, IIT Gandhinagar
        \item Publication : ABC, IOT IEEE Transactions (Impact Factor: 9.3, Status: Published)
        \item Student President, Technology and Research, IIT Gandhinagar
        \item Publication : ABC, IOT IEEE Transactions (Impact Factor: 9.3, Status: Published)
        \item Student President, Technology and Research, IIT Gandhinagar
        \item Publication : ABC, IOT IEEE Transactions (Impact Factor: 9.3, Status: Published)
    \end{rSection}


\end{document}
