%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[9pt]{src/developercv}
\usepackage{src/tailwindcolors}
\usepackage{enumitem}
\usepackage{changepage}
%----------------------------------------------------------------------------------------

\begin{document}
  \pagecolor{white}
  %----------------------------------------------------------------------------------------
  %	TITLE AND CONTACT INFORMATION
  %----------------------------------------------------------------------------------------
  \colorbox{sky900}{\hspace{0.3cm}\HUGE\textcolor{white}{\textbf{\MakeUppercase{Nasif}}}\hspace{0.3cm}}
  \colorbox{sky800}{\hspace{0.3cm}\HUGE\textcolor{white}{\textbf{\MakeUppercase{Mauthoor}}}\hspace{0.3cm}}
  
  \vspace{0.1cm}
  \vcenteredhbox{\colorbox{sky800}{\makebox(10, 10){\textcolor{white}{\Large\csname faMapMarker\endcsname}}}}
  \hspace{0.1cm}
  \vcenteredhbox{\textcolor{black}{Oakville, Ontario}}
  \hfill
  \vcenteredhbox{\colorbox{sky700}{\makebox(10, 10){\textcolor{white}{\Large\csname faPhone\endcsname}}}}
  \hspace{0.1cm}
  \vcenteredhbox{\textcolor{black}{416-655-2083}}
  \hfill
  \vcenteredhbox{\colorbox{sky600}{\makebox(10, 10){\textcolor{white}{\Large\csname faAt\endcsname}}}}
  \hspace{0.1cm}
  \vcenteredhbox{\textcolor{black}{\href{mailto:info@nasifmauthoor.com}{info@nasifmauthoor.com}}}
  \hfill
  \vcenteredhbox{\colorbox{sky400}{\makebox(10, 10){\textcolor{white}{\Large\csname faGithub\endcsname}}}}
  \hspace{0.1cm}
  \vcenteredhbox{\textcolor{black}{\href{https://github.com/Na51f}{github.com/Na51f}}}
  
  \vspace{0.5cm}
  {\huge Systems Administrator \& IT Support Specialist}
  %----------------------------------------------------------------------------------------

  %----------------------------------------------------------------------------------------
  %	PROFESSIONAL SUMMARY
  %----------------------------------------------------------------------------------------
  \vspace{\baselineskip}
  \colorbox{sky950}{\textcolor{white}{\LARGE\MakeUppercase{\textbf{Professional Summary}}}}
  \begin{itemize}[leftmargin=2em, itemsep=0.1em]
    \item Proficient in deploying and troubleshooting Windows 11, iOS, MacOS,
    Linux, and Android systems.
    \item Skilled in hardware diagnostics, automated software deployment, and
    patch management.
    \item Experienced with Mobile Device Management (MDM) and advanced
    bootloader configuration.
  \end{itemize}
  %----------------------------------------------------------------------------------------

  %----------------------------------------------------------------------------------------
  %	EDUCATION AND CERTIFICATIONS
  %----------------------------------------------------------------------------------------
  \vspace{\baselineskip}
  \colorbox{sky900}{\textcolor{white}{\LARGE\MakeUppercase{\textbf{Education \& Certifications}}}}
  \begin{itemize}[leftmargin=2em, itemsep=0.1em]
    % End date: 2027
    \item G-Class Driver's License, Ontario \hfill Valid until 2027
    % End date: 2025
    \item Generative AI for Software Developers from IBM \hfill Completed 2025
    \item B.Eng, Computer Engineering (CO-OP) from University of Guelph
    \hfill Graduating 2025
    % End date: 2022
    \item Introduction to Web Development from University of California, Davis
    \hfill Completed 2022
    % End date: 2019
    \item Bilingual High School Diploma from Jeunes Sans Frontières
    \hfill Graduated 2019
  \end{itemize}
  %----------------------------------------------------------------------------------------

  %----------------------------------------------------------------------------------------
  %	WORK EXPERIENCE
  %----------------------------------------------------------------------------------------
  \vspace{\baselineskip}
  \colorbox{sky900}{\textcolor{white}{\LARGE\MakeUppercase{\textbf{Work Experience}}}}
  
  \vspace{1.0\baselineskip}

  % End date: Present
  \textit{Project Lead \& Systems Administrator, CoCreCo University of Guelph,
  Guelph, ON} \hfill \textit{2025 to Present}
  \begin{itemize}[leftmargin=2em, itemsep=0.1em]
    \item Managed and administered the computing infrastructure for a large-scale
    agricultural research project, supporting over 50 researchers.
    \item Deployed and managed virtual machines and system images using
    \textbf{Windows 11} and server administration tools, creating the scalable
    infrastructure for a \$20,000 research system.
    \item Configured and deployed containerized software environments using
    \textbf{Docker} on Linux systems, reducing system setup time for new team
    members from 4 hours to 15 minutes.
    \item Implemented machine learning models using \textbf{Python and
    TensorFlow}, delivering an 85\% accuracy improvement in pest detection
    algorithms used by students.
  \end{itemize}

  \vspace{1.0\baselineskip}

  % End date: Present
  \textit{Computer Science Tutor \& IT Support Specialist, Bright Learning
  Center \& Cloud Times Global, Oakville, ON} \hfill \textit{2022 to Present}
  \begin{itemize}[leftmargin=2em, itemsep=0.1em]
    \item Provided direct technical support and instruction to students, helping
    them set up and troubleshoot their computer systems and software.
    \item Performed hands-on \textbf{hardware and software troubleshooting} for
    students' Windows and macOS laptops, resolving development environment
    issues and reducing setup problems by 80\%.
    \item Managed the \textbf{installation and configuration} of various software
    development tools (IDEs, compilers) across multiple operating systems,
    ensuring students had functional learning environments.
    \item Organized teaching resources and created standardized documentation
    used by 3 other tutoring centers to streamline curriculum delivery.
  \end{itemize}

  \vspace{1.0\baselineskip}

  % End date: 2023
  \textit{System Administrator \& IT Support Lead, Ddrops Company, Vaughan, ON}
  \hfill \textit{2022 to 2023}
  \begin{itemize}[leftmargin=2em, itemsep=0.1em]
    \item Provided comprehensive IT support and system administration for company
    operations, focusing on device management, software deployment, and
    infrastructure maintenance.
    \item Deployed and configured software on \textbf{Windows 11} workstations
    for the QA team, creating standardized testing environments that reduced
    manual setup time by 70\%.
    \item Administered document management systems and automated workflows using
    \textbf{Microsoft Power Automate}, saving an estimated 15 hours of manual
    work per week.
    \item Authored and maintained technical documentation and support guides,
    reducing onboarding time for new users and standardizing troubleshooting
    procedures.
  \end{itemize}

  \vspace{1.0\baselineskip}

  % End date: 2022
  \textit{IT Support Technician \& Service Representative, ClaimsPro \& Reliance
  Home Comfort, Mississauga, ON} \hfill \textit{2019 to 2022}
  \begin{itemize}[leftmargin=2em, itemsep=0.1em]
    \item Delivered frontline technical support and customer service, managing
    client data and coordinating with field technicians for hardware and
    software issues.
    \item Provided technical support for both desktop systems and mobile devices,
    including \textbf{iOS} phones and tablets used by field technicians for
    scheduling and communication.
    \item Maintained customer records and claim processing systems using
    \textbf{SQL} database management, achieving a 99.5\% data accuracy rate
    across over 1,000 monthly claims.
    \item Created user-friendly support guides in \textbf{HTML and Markdown} for
    internal software, reducing new employee training time on core systems by
    40\%.
  \end{itemize}
  %----------------------------------------------------------------------------------------

  %----------------------------------------------------------------------------------------
  %	PROJECTS
  %----------------------------------------------------------------------------------------
  \vspace{\baselineskip}
  \colorbox{sky800}{\textcolor{white}{\LARGE\MakeUppercase{\textbf{Current Projects}}}}

  \vspace{1.0\baselineskip}
  
  % End date: Present
  \textit{Custom Micro-controller Powered 3D printed Keyboard, Personal Project,
  Oakville, ON} \hfill \textit{2025 to Present}
  \begin{itemize}[leftmargin=2em, itemsep=0.1em]
    \item Built custom mechanical keyboard from scratch, designing ergonomic
    layout optimized for programming efficiency.
    \item Programmed custom key mappings and macros using C++ and QMK Firmware,
    creating personalized Colemak DH layout that improved typing speed by 25\%.
    \item Integrated Kailh Choc switches with custom PCB through VHDL and
    hardware design, developing fully functional 60\% keyboard with programmable
    features.
  \end{itemize}

  \vspace{1.0\baselineskip}
  
  % End date: Present
  \textit{Multi-Platform Streaming for Businesses, Personal Project, Oakville,
  ON} \hfill \textit{2024 to Present}
  \begin{itemize}[leftmargin=2em, itemsep=0.1em]
    \item Developed comprehensive streaming platform aggregator to help
    businesses manage multiple social media channels from single interface.
    \item Built full-stack web application using T3 Stack (TypeScript, React,
    Next.js), creating scalable platform supporting simultaneous streaming to 3+
    platforms.
    \item Connected Twitch, YouTube, and TikTok streaming services through API
    integration, automating content distribution and reducing manual posting
    time by 80\%.
    \item Implemented responsive UI with database and authentication using
    TailwindCSS, Prisma, and Clerk, delivering professional-grade platform with
    user management capabilities.
  \end{itemize}

  \vspace{\baselineskip}
  \colorbox{sky700}{\textcolor{white}{\LARGE\MakeUppercase{\textbf{Academic Projects}}}}

  \vspace{1.0\baselineskip}
  
  % End date: 2022
  \textit{Computer Systems Programming Projects, University of Guelph, Guelph,
  ON} \hfill \textit{2021 to 2022}
  \begin{itemize}[leftmargin=2em, itemsep=0.1em]
    \item Completed advanced systems programming coursework, building low-level
    computing components and operating system features.
    \item Designed virtual CPU executing MARS MIPS assembly using C and VHDL,
    creating functional processor simulation with registers and multiplexers.
    \item Developed thread and process scheduler in C for operating systems,
    implementing memory management system handling concurrent processes
    efficiently.
    \item Built custom shell with I/O pipelining through BASH shell development,
    creating command-line interface supporting background processes and advanced
    features.
  \end{itemize}

  \vspace{1.0\baselineskip}
  
  % End date: 2019
  \textit{Teddy-Bear Wheelchair Competition, University of Guelph, Guelph, ON}
  \hfill \textit{2019}
  \begin{itemize}[leftmargin=2em, itemsep=0.1em]
    \item Engineered autonomous robotic wheelchair for engineering competition,
    integrating precision shooting mechanism with navigation system.
    \item Programmed robotic control systems using C++ and Arduino, achieving
    90\% accuracy in ping-pong ball shooting mechanism during competition
    trials.
    \item Implemented path-finding algorithms for autonomous navigation,
    successfully completing obstacle course challenges in under 3 minutes.
  \end{itemize}
  %----------------------------------------------------------------------------------------

  %----------------------------------------------------------------------------------------
  %	LANGUAGES
  %----------------------------------------------------------------------------------------
  \vspace{\baselineskip}
  \colorbox{sky600}{\textcolor{white}{\LARGE\MakeUppercase{\textbf{Languages}}}}
  \begin{itemize}[leftmargin=2em, itemsep=0.1em]
    \item \textbf{English} - Native, Fluent
    \item \textbf{French} - Native, Fluent
  \end{itemize}
  \vspace{1.0\baselineskip}
  %----------------------------------------------------------------------------------------

  %----------------------------------------------------------------------------------------
  %	REFERENCES
  %----------------------------------------------------------------------------------------
  \colorbox{sky500}{\textcolor{white}{\LARGE\MakeUppercase{\textbf{References}}}}\\\\
  {\large References available upon request}
  %----------------------------------------------------------------------------------------
\end{document}